\documentclass[../butidigress.tex]{subfiles}

\begin{document}
\chapter{Quotations}\label{chap:quotations}
\newpage
\newlength{\episkip}
\setlength{\episkip}{0.5cm}
% \newcommand{\postepi}{\vspace{\episkip}\noindent\hfill\rule{\textwidth}{0.1em}\hfill\vspace{\episkip}}
\newcommand{\postepi}{}
% https://en.wikiquote.org/wiki/Truth
% https://en.wikiquote.org/wiki/Skepticism
% https://en.wikiquote.org/wiki/Knowledge
% https://en.wikiquote.org/wiki/Science
% https://en.wikiquote.org/wiki/History_of_science
% https://en.wikiquote.org/wiki/Atomic_theory
% https://en.wikiquote.org/wiki/Immanuel_Kant
% https://en.wikiquote.org/wiki/Malcolm_X
% https://en.wikiquote.org/wiki/Martin_Luther_King,_Jr.
\lettrine{S}{ome} quotations that I decided to not use as epigraphs (and also other quotes that I like).
Honestly, some of these may be upgraded to epigraph status; for example, I had a Camus quote from \textit{The Myth of Sisyphus}, which is now on page~\pageref{sec:voidexpounding}

The quotations may seem, to some to be kinda cheesy, or indicative of me not being able to come up with all of my own ideas, but to me they are focusing, they remind me about what I'm trying to write.
That's why I've put a pretty decent amount of time into selecting each one.

\par\postepi
\epigraph{Tonight, we gather to affirm the greatness of our nation---not because of the height of our skyscrapers, or the power of our military, or the size of our economy. Our pride is based on a very simple premise, summed up in a declaration made over two hundred years ago: `We hold these truths to be self-evident, that all men are created equal, that they are endowed by their Creator with certain inalienable rights, that among these are life, liberty, and the pursuit of happiness.' That is the true genius of America---a faith in simple dreams, an insistence on small miracles.}{\attrib{Barack Obama}{DNC Keynote Speech}{2004}}
\postepi
\epigraph{The best episodes of \tvshow{The West Wing} that dealt with policy and stuff, in my opinion, were the ones where they were in the middle of a crisis, and they were trying to figure out how to solve problems.}{\textsc{Michael Schur}}
\postepi
\epigraph{The best shows are always the ones that are very, very low-concept and just about great characters.}{\textsc{Michael Schur}}
\postepi
\epigraph{You should be nice to people because it's better to be nice to people than mean to people, not because you think there's something in it for you.}{\textsc{Michael Schur}}
\postepi
\epigraph{There's no way to approach anything in an objective way. We're completely subjective; our view of the world is completely controlled by who we are as human beings, as men or women, by our age, our history, our profession, by the state of the world.}{\textsc{Charlie Kaufman}}
\postepi
\epigraph{It occurred to me that every work of art is a synecdoche, there's no way around it. Every creative work that someone does can only represent an aspect of the whole of something. I can't think of an exception to that.}{\textsc{Charlie Kaufman}}
\postepi
\epigraph{Happiness is not an ideal of reason but of imagination}{\attrib{Immanuel Kant}{Fundamental Principles of the Metaphysics of Ethics}{1785}}
\postepi
\epigraph{Science is the belief in the ignorance of experts.}{\textsc{Richard Feynman}}
\postepi
\epigraph{No union is more profound than marriage, for it embodies the highest ideals of love, fidelity, devotion, sacrifice, and family. In forming a marital union, two people become something greater than once they were. As some of the petitioners in these cases demonstrate, marriage embodies a love that may endure even past death. It would misunderstand these men and women to say they disrespect the idea of marriage. Their plea is that they do respect it, respect it so deeply that they seek to find its fulfillment for themselves. Their hope is not to be condemned to live in loneliness, excluded from one of civilization's oldest institutions. They ask for equal dignity in the eyes of the law. The Constitution grants them that right.\par\hspace*{2em} The judgment of the Court of Appeals for the Sixth Circuit is reversed. \par\hfill \textit{It is so ordered.}}{\attrib{Justice Anthony Kennedy}{Obergefell v.\ Hodges}{2015}}
\postepi
\epigraph{\ldots The point is to entertain people, and make them forget that we are all dying in front of each other, that this is just this horrible rotten slog to rigor mortis, that we are going to lose everybody we know, we are going to lose everything we have. And the only way to distract ourselves is by separating our day into distractions.}{\textsc{Sam Miller\ftnote{I assume.}}, \textit{Effectively Wild}}
\postepi
\epigraph{The life of the law has not been logic: it has been experience.}{\attrib{Oliver Wendell Holmes Jr.}{The Common Law}{1881}}
\postepi
\epigraph{Those who won our independence believed that the final end of the state was to make men free to develop their faculties, and that in its government the deliberative forces should prevail over the arbitrary. They valued liberty both as an end and as a means. They believed liberty to be the secret of happiness and courage to be the secret of liberty. They believed that freedom to think as you will and to speak as you think are means indispensable to the discovery and spread of political truth; that without free speech and assembly discussion would be futile; that with them, discussion affords ordinarily adequate protection against the dissemination of noxious doctrine; that the greatest menace to freedom is an inert people; that public discussion is a political duty; and that this should be a fundamental principle of the American government.}{\attrib{Louis Brandeis}{Concurring, Whitney v.\ California}{1927}}
\end{document}